Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Fix spelling and grammar errors

Just as in CCT, our bias correction step introduces additional
variability. However, the second order polynomial again adequately estimates the
features of the true DGP that are necessary for estimating and accommodating that
additional variability. So we propose
an iterated bootstrap procedure \citep{hall1988}: use the second order
polynomial bootstrap to produce many bootstrap replications of the bias
corrected estimator, and then use the resulting bootstrap distribution to
produce confidence intervals. This procedure, which requires bootstrapping the
datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}
and the resulting confidence intervals are shown to be asymptotically valid in
Theorem~\ref{T2}.\footnote{%
  Since our bootstrap resamples the residuals but not the running variable, many
  of the quantities used to prodcue the estimates do not change under the
  bootstrap distribution and can be reused from the original
  estimate. Exploiting this feature makes the iterated bootstrap much less
  computationally burdensome; see the discussion following
  Algoritnm~\ref{Alg2}.} %

@@

Panel B presents results for the heteroskedastic case. The coverages obtained are similar to those in Panel A and highlight 
the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
similarly and have coverage close to the nominal level. The bootstrap explicitly
accounts for heterosedasticity in the DGP; CCT's procedure implicitly accomodates
smooth heteroskedasticity by estimating the variance in a neighborhood around
the cutoff.

@@

The two robust procedures are again very similar to each other and give
statistically significant, positve, estimates. The confidence intervals tend to shift
relative to the original intervals, increasing both the range of effects consistent
with the data as well as the lower bound on plausible effects.
In contrast to the striking differences between the conventional
and bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.

>>>>

Just as in CCT, our bias correction step introduces additional
variability. However, the second order polynomial again adequately estimates the
features of the true DGP that are necessary for estimating and accommodating that
additional variability. So we propose
an iterated bootstrap procedure \citep{hall1988}: use the second order
polynomial bootstrap to produce many bootstrap replications of the bias
corrected estimator, and then use the resulting bootstrap distribution to
produce confidence intervals. This procedure, which requires bootstrapping the
datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}
and the resulting confidence intervals are shown to be asymptotically valid in
Theorem~\ref{T2}.\footnote{%
  Since our bootstrap resamples the residuals but not the running variable, many
  of the quantities used to produce the estimates do not change under the
  bootstrap distribution and can be reused from the original
  estimate. Exploiting this feature makes the iterated bootstrap much less
  computationally burdensome; see the discussion following
  Algorithm~\ref{Alg2}.} %

@@

Panel B presents results for the heteroskedastic case. The coverage obtained is similar to that in Panel A and highlight
the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
similarly and have coverage close to the nominal level. The bootstrap explicitly
accounts for heterosedasticity in the DGP; CCT's procedure implicitly accommodates
smooth heteroskedasticity by estimating the variance in a neighborhood around
the cutoff.

@@

The two robust procedures are again very similar to each other and give
statistically significant, positive, estimates. The confidence intervals tend to shift
relative to the original intervals, increasing both the range of effects consistent
with the data as well as the lower bound on plausible effects.
In contrast to the striking differences between the conventional
and bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.
